%-------------------------
% Resume in Latex
% Author : Resumind Example
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Prianka Sharma} \\ \vspace{1pt}
    \small 415-555-0921 $|$ \href{mailto:prianka.data@email.com}{\underline{prianka.data@email.com}} $|$ 
    \href{https://linkedin.com/in/priankasharma}{\underline{linkedin.com/in/priankasharma}} $|$
    \href{https://github.com/priankadata}{\underline{github.com/priankadata}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Master of Computational Data Science}{Aug. 2019 -- Dec 2020}
    \resumeSubheading
      {Indian Institute of Technology, Bombay}{Mumbai, India}
      {Bachelor of Technology in Computer Science}{July 2015 -- May 2019}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Data Scientist}{Jan 2021 -- Present}
      {FinTech Global}{New York, NY}
      \resumeItemListStart
        \resumeItem{Developed and deployed a fraud detection model using XGBoost and AWS SageMaker, preventing \$2M in fraudulent transactions annually.}
        \resumeItem{Led a team of 4 data scientists to build a customer churn prediction pipeline, improving retention rates by 15\% via targeted interventions.}
        \resumeItem{Engineered a real-time recommendation system handling 10k requests/second using Apache Spark and Kafka.}
        \resumeItem{Collaborated with product teams to design A/B tests quantifying the impact of new features on user engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{May 2020 -- Aug 2020}
      {HealthAI Inc.}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Analyzed patient electronic health records (EHR) to predict readmission risks using Logistic Regression and Random Forest models.}
        \resumeItem{Cleaned and preprocessed a dataset of 1M+ records using Pandas and NumPy, reducing missing values by imputation techniques.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Stock Market Sentiment Analysis} $|$ \emph{Python, NLP, BERT}}{Sep 2020}
          \resumeItemListStart
            \resumeItem{Fine-tuned a BERT model on financial news headlines to classify market sentiment with 89\% accuracy.}
            \resumeItem{Built a dashboard using Streamlit to visualize sentiment trends alongside stock price movements.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Image Caption Generator} $|$ \emph{TensorFlow, LSTM, CNN}}{Apr 2020}
          \resumeItemListStart
            \resumeItem{Implemented an encoder-decoder architecture with attention mechanisms to generate descriptive captions for images.}
            \resumeItem{Trained on the COCO dataset and achieved a BLEU score of 0.65.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, R, Scala, Bash, C++} \\
     \textbf{Machine Learning}{: PyTorch, TensorFlow, Scikit-learn, XGBoost, Keras, NLTK, Spacy} \\
     \textbf{Big Data & Cloud}{: AWS (S3, EC2, SageMaker), Spark, Hadoop, SQL, Snowflake, Docker, Kubernetes} \\
     \textbf{Visualization}{: Tableau, PowerBI, Matplotlib, Seaborn, Plotly}
    }}
 \end{itemize}

\end{document}
