%-------------------------
% Resume in Latex
% Author : Resumind Example
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Alex Morgan} \\ \vspace{1pt}
    \small 555-010-2345 $|$ \href{mailto:alex.morgan@email.com}{\underline{alex.morgan@email.com}} $|$ 
    \href{https://linkedin.com/in/alexmorgan}{\underline{linkedin.com/in/alexmorgan}} $|$
    \href{https://alexmorgan.design}{\underline{alexmorgan.design}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {Bachelor of Arts in Cognitive Science, Certificate in Design Innovation}{Aug. 2018 -- May 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Product Designer}{June 2022 -- Present}
      {TechStream Solutions}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Led the end-to-end redesign of the core enterprise dashboard, resulting in a 25\% increase in user engagement and 15\% reduction in support tickets.}
        \resumeItem{Collaborated closely with Product Managers and Engineering to define product strategy and roadmap, ensuring design feasibility and business alignment.}
        \resumeItem{Established and maintained the robust "StreamLine" design system in Figma, improving design-to-dev handoff efficiency by 40\%.}
        \resumeItem{Conducted user research studies including 20+ user interviews and usability tests to validate new feature concepts.}
      \resumeItemListEnd

    \resumeSubheading
      {Product Design Intern}{May 2021 -- Aug 2021}
      {Creative Cloud Inc.}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Designed and prototyped a new mobile onboarding flow for 500k+ new monthly users, reducing drop-off rates by 12\%.}
        \resumeItem{Created high-fidelity mockups and interactive prototypes using Figma and Principle for weekly stakeholder reviews.}
        \resumeItem{Partnered with the accessibility team to audit and improve contrast ratios across the mobile application.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{EcoTrack App} $|$ \emph{Figma, iOS, User Research}}{Jan 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Designed a mobile application to help users track their carbon footprint, winning "Best Design" at UC Berkeley Hackathon.}
            \resumeItem{Conducted competitive analysis and user journey mapping to identify key pain points in existing sustainability apps.}
            \resumeItem{Developed a clickable prototype used to pitch to local environmental non-profits.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Design}{: Figma, Adobe Creative Suite (XD, Illustrator, Photoshop), Sketch, Principle, Prototyping, Wireframing} \\
     \textbf{Research}{: Usability Testing, User Interviews, A/B Testing, Heuristic Evaluation, User Personas, Journey Maps} \\
     \textbf{Development}{: HTML, CSS, Basic JavaScript, Webflow} \\
     \textbf{Collaboration}{: Jira, Notion, Slack, Miro, Agile/Scrum}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
