%-------------------------
% Resume in Latex
% Author : Resumind Example
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Michael Chen} \\ \vspace{1pt}
    \small 206-555-0199 $|$ \href{mailto:michael.pm@email.com}{\underline{michael.pm@email.com}} $|$ 
    \href{https://linkedin.com/in/michaelchenpm}{\underline{linkedin.com/in/michaelchenpm}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Stanford, CA}
      {Master of Business Administration (MBA)}{Sep. 2018 -- June 2020}
    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Bachelor of Science in Computer Engineering}{Sep. 2012 -- May 2016}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Product Manager}{July 2020 -- Present}
      {Streamline SaaS}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Owned the product roadmap for the Core Automation Platform, launching 3 major features that drove \$5M in incremental ARR.}
        \resumeItem{Conducted market research and competitor analysis to identify a gap in the SMB market, leading to the development of "Streamline Lite".}
        \resumeItem{Facilitated cross-functional collaboration between Engineering, Design, and Sales teams to ensure on-time delivery of quarterly goals.}
        \resumeItem{Analyzed user behavior data using Mixpanel to optimize the onboarding flow, increasing activation rates by 22\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Product Manager}{June 2016 -- Aug 2018}
      {AutoTech Solutions}{Detroit, MI}
      \resumeItemListStart
        \resumeItem{Managed the lifecycle of the "SmartDash" infotainment system from concept to launch across 3 vehicle models.}
        \resumeItem{Prioritized backlog items based on RICE scoring method, balancing technical debt with new feature development.}
        \resumeItem{Worked closely with QA to reduce critical bugs by 50% prior to release candidate freeze.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Community Garden App} $|$ \emph{Side Project}}{Jan 2019 -- Present}
          \resumeItemListStart
            \resumeItem{Launched a mobile app connecting local gardeners with available plots of land.}
            \resumeItem{Grew user base to 2,000 active monthly users with zero marketing budget through organic community engagement.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Product Strategy}{: Roadmap Planning, Vision Setting, Market Research, Competitor Analysis, Go-to-Market Strategy} \\
     \textbf{Execution}{: Agile/Scrum, JIRA, User Stories, Backlog Prioritization, A/B Testing, MVP Development} \\
     \textbf{Analytics}{: SQL, Tableau, Google Analytics, Mixpanel, Amplitude} \\
     \textbf{Tools}{: Figma, Notion, Slack, Confluence, Trello}
    }}
 \end{itemize}

\end{document}
