%-------------------------
% Resume in Latex
% Author : Resumind Example
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Sarah Jenkins} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:sarah.dev@email.com}{\underline{sarah.dev@email.com}} $|$ 
    \href{https://linkedin.com/in/sarahjenkins}{\underline{linkedin.com/in/sarahjenkins}} $|$
    \href{https://github.com/sarahcodes}{\underline{github.com/sarahcodes}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science}{Aug. 2020 -- May 2022}
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Bachelor of Science in Computer Science}{Aug. 2016 -- May 2020}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Frontend Engineer}{June 2022 -- Present}
      {CloudScale Dynamics}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Architected and laid the groundwork for a new SaaS analytics platform using Next.js, React, and TypeScript, scaling to 10k+ daily users.}
        \resumeItem{Improved application performance by 35\% through code splitting, image optimization (WebP), and server-side rendering (SSR).}
        \resumeItem{Mentored 3 junior developers, conducting code reviews and instituting TDD practices that reduced production bugs by 20\%.}
        \resumeItem{Collaborated with UX teams to implement complex data visualizations using D3.js and Recharts.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July 2020 -- May 2022}
      {Nexus Systems}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Developed responsive web applications using React and Redux for a logistics management system.}
        \resumeItem{Integrated RESTful APIs and transitioned legacy codebase to use GraphQL, reducing network payload size by 40\%.}
        \resumeItem{Automated deployment pipelines using Docker and Jenkins, achieving continuous delivery for the frontend team.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AniSearch} $|$ \emph{React, Tailwind, AniList API}}{Oct 2021}
          \resumeItemListStart
            \resumeItem{Built a real-time anime discovery engine with advanced filtering and search capabilities.}
            \resumeItem{Implemented infinite scrolling and optimistic UI updates for a seamless user experience.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TaskMaster CLI} $|$ \emph{Node.js, Commander.js, MongoDB}}{Jan 2021}
          \resumeItemListStart
            \resumeItem{Created a developer-focused command-line tool for task management and time tracking.}
            \resumeItem{Published to NPM with over 500+ weekly downloads.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript (ES6+), Python, HTML5, CSS3/SCSS, SQL} \\
     \textbf{Frameworks/Libraries}{: React, Next.js, Vue.js, Node.js, Express, Tailwind CSS, Jest, Cypress} \\
     \textbf{Tools}{: Git, Docker, AWS (S3, CloudFront), Figma, Webpack, Vercel} \\
     \textbf{Concepts}{: REST API, GraphQL, CI/CD, Agile Methodology, Responsive Design}
    }}
 \end{itemize}

\end{document}
