%-------------------------
% Resume in Latex
% Author : Resumind Example
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jordan Lee} \\ \vspace{1pt}
    \small 987-654-3210 $|$ \href{mailto:jordan.ui@email.com}{\underline{jordan.ui@email.com}} $|$ 
    \href{https://dribbble.com/jordanlee}{\underline{dribbble.com/jordanlee}} $|$
    \href{https://jordanlee.portfolio}{\underline{jordanlee.portfolio}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Parsons School of Design}{New York, NY}
      {Bachelor of Fine Arts in Communication Design}{Aug. 2017 -- May 2021}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Lead UI Designer}{May 2021 -- Present}
      {PixelPerfect Agency}{New York, NY}
      \resumeItemListStart
        \resumeItem{Designed high-conversion landing pages and marketing assets for Fortune 500 clients, achieving an average conversion rate uplift of 18\%.}
        \resumeItem{Spearheaded the visual redesign of a fintech mobile app, focusing on micro-interactions and accessibility (WCAG 2.1 AA).}
        \resumeItem{Created and maintained a comprehensive UI Kit and Design System, reducing design consistency errors by 90\%.}
        \resumeItem{Partnered with motion designers to create custom Lottie animations that enhanced user delight and retention.}
      \resumeItemListEnd

    \resumeSubheading
      {Visual Design Intern}{June 2020 -- Aug 2020}
      {Studio G}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Assisted in the branding and identity creation for 3 startups, including logo design and color palette selection.}
        \resumeItem{Designed social media assets and email templates that aligned with established brand guidelines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NeoBank Mobile App} $|$ \emph{Figma, ProtoPie}}{Sep 2021}
          \resumeItemListStart
            \resumeItem{Designed a concept banking app focusing on dark mode aesthetics and simplified transaction flows.}
            \resumeItem{Created a high-fidelity prototype demonstrating complex gesture-based interactions.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Traveler Web Portal} $|$ \emph{Adobe XD, Webflow}}{Jan 2021}
          \resumeItemListStart
            \resumeItem{Designed and built a responsive travel blog website using Webflow, featuring custom CMS layout and interactions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Expertise}{: UI Design, Visual Design, Interaction Design, Prototyping, Wireframing, Branding, Typography, Color Theory} \\
     \textbf{Tools}{: Figma, Adobe XD, Sketch, Photoshop, Illustrator, After Effects, ProtoPie, Webflow} \\
     \textbf{Languages}{: HTML, CSS, Basic JavaScript}
    }}
 \end{itemize}

\end{document}
